---
# title: "`r params$area_name`"
title: ""
author: ""
date: ""
# date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  area_num: 5
  area_name: "Temp Name"
geometry: margin=2cm
output:
  pdf_document
linkcolor: blue
# header-includes:
#   - \usepackage{caption}
#   - \captionsetup[figure]{labelformat=empty}
# editor_options: 
#   chunk_output_type: console
# knit: (function(inputFile, encoding){ 
#     out_dir <- '/';
#     rmarkdown::render(inputFile, encoding = encoding, output_file=file.path(dirname(inputFile), out_dir, 'ECOL592_RDAandCCA_GWoolsey.pdf')) 
#   })
---

```{r, include=F, warning=F, message=F, echo=F}
# knit options
knitr::opts_chunk$set(
  echo = FALSE
  , warning = FALSE
  , message = FALSE
  , include = TRUE
  , eval = TRUE
  , fig.asp = 0.8
  , fig.width = 7
  # , fig.height = 8
  , fig.align = 'center'
)
remove(list = ls()[grep("_temp",ls())])
gc()
```

```{r call-fns}
##################################################
##################################################
# set the figure size
##################################################
##################################################
bb_temp <- wf_landscapes %>% 
  dplyr::filter(area_name==area_nm_list[params$area_num]) %>% 
  sf::st_transform(3857) %>% 
  sf::st_bbox()
w_temp <- bb_temp[3] - bb_temp[1]
h_temp <- bb_temp[4] - bb_temp[2]
# fig.asp sets the height-to-width ratio
image_asp_temp <- min(h_temp/w_temp,1)
# fix for layered constraints text sizing
base_size_temp = ifelse(image_asp_temp==1,8,9)
ggtext_size_temp = ifelse(image_asp_temp==1,7,10)
# width_for_image <- round(((21.59-2*2)/2.54),1) # max width of 21.59cm page with 2cm margin (converted to in)
# height_for_image_temp <- round((width_for_image * h_temp) / w_temp, 1)
##################################################
##################################################
# call all the functions
##################################################
##################################################
# set aggregate factor for raster data
  agg_fact_temp <- 20
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  plt_basemap <<- landscape_basemap_fn(row_n = params$area_num, my_base_size = base_size_temp)
# load raster data
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  rast_list_temp <<- raster_data_read_fn(row_n = params$area_num)
  # rast_list_temp <- raster_data_read_fn(row_n = params$area_num)
#################
# PLOTS
#################
title_plot_temp <- title_plot_fn(row_n = params$area_num)
# spatial_frmwrk_map_temp <- spatial_frmwrk_map_fn(row_n = params$area_num)
spatial_frmwrk_inset_temp <- spatial_frmwrk_inset_fn(row_n = params$area_num)
# rast_area_fn(row_n = params$area_num, layer_name = "is_treatable")
landcover_map_temp <- landcover_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
protected_map_temp <- protected_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
slopes_map_temp <- slopes_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
roads_map_temp <- roads_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
riparian_map_temp <- riparian_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
administrative_map_temp <- administrative_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
# tables
reduction_table_temp <- reduction_table_fn(row_n = params$area_num)
reduction_kable_temp <- reduction_kable_fn(row_n = params$area_num)

# names and labels
area_name_nost <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(name)
area_st <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(state)
area_acres <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(acres) %>% 
  scales::comma(suffix = "k", scale = 1e-3, accuracy = 1)
area_ha <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(hectares) %>% 
  scales::comma(suffix = "k", scale = 1e-3, accuracy = 1)
```

```{r print-title, fig.height=1, fig.width=10, fig.asp=NULL, fig.align='left'}
title_plot_temp
```

```{r print-spatial-frmwrk, fig.asp=image_asp_temp}
# {r print-spatial-frmwrk, fig.height=height_for_image_temp, fig.width=width_for_image}
# spatial_frmwrk_map_temp
spatial_frmwrk_inset_temp +
  theme(
    # plot.title = element_blank()
    plot.margin = margin(0,0,0,0,"cm")
  )
```

The `r area_name_nost` priority landscape (black outline) located in `r area_st` (see map inset) covers `r area_acres` acres (`r area_ha` ha). This analysis utilized the nested spatial framework delineating firesheds (gray dashed outline) approximately 250,000 acres (100,000 ha) in size which are the broad scale unit of prioritization and nested fireshed project areas (light blue outline) approximately 25,000 acres (10,000 ha) in size which are used for planning and conducting fuel management projects. Fireshed project areas are shaded by risk to communities of the parent fireshed with the highest risk firesheds as determined by the USFS Wildfire Crisis Strategy shaded red (multiple ownerships) and orange (USFS ownership only). The full process for delineating fireshed boundaries and determining risk across the continental US is described in detail in [Ager et al. (2021)](https://scholar.google.com/scholar?cluster=7852635540589253195&hl=en&as_sdt=0,6).

```{r print-layered-constraints}
(landcover_map_temp + 
  protected_map_temp + 
  slopes_map_temp + 
  roads_map_temp + 
  riparian_map_temp + 
  administrative_map_temp) +
  patchwork::plot_layout(
    ncol = 3
    # , widths = c(1, 2)
  ) +
  patchwork::plot_annotation(tag_levels = 'A') & 
  theme(
    plot.title = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
    , plot.subtitle = ggtext::element_markdown(size = ggtext_size_temp)
  )  
# to get plots to overlap ;)
# G3 <- G1 + plot_spacer() + G2 + plot_layout(widths = c(4, -1.1 ,4.5),guides = "collect")& theme(legend.position = "top")
```

Layered operational constraints were considered in order to quantify the amount of land available for mechanical forest health and risk reduction fuel treatments. The analysis identifies (A) all forest and shrubland areas, (B) removes protected and inventoried roadless areas (IRA), (C) classifies land as mechanically operable based on terrain slope, (D) buffers existing roads according to equipment haul distance, (E) removes areas within riparian buffers, (F) removes areas within administrative boundaries to determine what land is mechanically available or constrained and by what factor.

```{r table-reductions, fig.height=2, fig.width=9.5, fig.asp=NULL}
# ```{r table-reductions, fig.height=2}
# reduction_kable_temp
reduction_table_temp + 
  theme(
    plot.title = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
  )
```

