---
# title: "`r params$area_name`"
title: ""
author: ""
date: ""
# date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  area_num: 5
  area_name: "Temp Name"
geometry: margin=1.5cm
output:
  pdf_document: default
  # bookdown::pdf_document2
linkcolor: blue
header-includes: |
    \usepackage{fancyhdr}
    \pagestyle{fancy}
    \fancyhead{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[CO,CE]{`r params$area_name`}
    \fancyfoot[LE,RO]{\thepage}
# header-includes:
#   - \usepackage{caption}
#   - \captionsetup[figure]{labelformat=empty}
# editor_options: 
#   chunk_output_type: console
# knit: (function(inputFile, encoding){ 
#     out_dir <- '/';
#     rmarkdown::render(inputFile, encoding = encoding, output_file=file.path(dirname(inputFile), out_dir, 'ECOL592_RDAandCCA_GWoolsey.pdf')) 
#   })
---

```{r, include=F, warning=F, message=F, echo=F}
# knit options
knitr::opts_chunk$set(
  echo = FALSE
  , warning = FALSE
  , message = FALSE
  , include = TRUE
  , eval = TRUE
  , fig.asp = 0.8
  , fig.width = 7
  # , fig.height = 8
  , fig.align = 'center'
)
remove(list = ls()[grep("_temp",ls())])
gc()
```

```{r call-fns}
##################################################
##################################################
# set the figure size
##################################################
##################################################
bb_temp <- wf_landscapes %>% 
  dplyr::filter(area_name==area_nm_list[params$area_num]) %>% 
  sf::st_transform(3857) %>% 
  sf::st_bbox()
w_temp <- bb_temp[3] - bb_temp[1]
h_temp <- bb_temp[4] - bb_temp[2]
# fig.asp sets the height-to-width ratio
image_asp_temp <- min(h_temp/w_temp,1)
# change the sizing of the basemap using theme_light(base_size = base_size_temp)
base_size_temp = ifelse(image_asp_temp==1,8,9)
# change the subtitle labels created with ggtext for layered constraints plot
ggtext_size_temp = ifelse(image_asp_temp==1,7,10)
# change the fig.asp for the treatable_map_fn figure since this is now wider than single map
image_asp_facet_temp <- max(image_asp_temp*ifelse(image_asp_temp==1,0.65,0.55),0.35)
# width_for_image <- round(((21.59-2*2)/2.54),1) # max width of 21.59cm page with 2cm margin (converted to in)
# height_for_image_temp <- round((width_for_image * h_temp) / w_temp, 1)
##################################################
##################################################
# call all the functions
##################################################
##################################################
# set aggregate factor for raster data
  agg_fact_temp <- 20
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  plt_basemap <<- landscape_basemap_fn(row_n = params$area_num, my_base_size = base_size_temp)
# load raster data
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  rast_list_temp <<- raster_data_read_fn(row_n = params$area_num)
  # rast_list_temp <- raster_data_read_fn(row_n = params$area_num)
#################
# PLOTS
#################
title_plot_temp <- title_plot_fn(row_n = params$area_num)
# spatial_frmwrk_map_temp <- spatial_frmwrk_map_fn(row_n = params$area_num)
spatial_frmwrk_inset_temp <- spatial_frmwrk_inset_fn(row_n = params$area_num)
# names and labels
area_name_nost <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(name)
area_st <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(state)
area_acres <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(acres) %>% 
  scales::comma(suffix = "k", scale = 1e-3, accuracy = 1)
area_ha <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(hectares) %>% 
  scales::comma(suffix = "k", scale = 1e-3, accuracy = 1)
####### high-risk area calculations
# usfs vs all lands
hi_risk_brkdwn_temp <-
  constrained_by_scnro_ls_pa %>% 
    dplyr::filter(
      pct_pa_intrsct>=0.25
      # & area_name == area_nm_list[19]
      & area_name == area_nm_list[params$area_num]
      & fireshed_crisis_strategy %in% c("USFS-Only", "All-Lands")
      & scenario_id == 1
    ) %>% 
    dplyr::group_by(fireshed_crisis_strategy) %>% 
    dplyr::summarise(
      n = n()
      , dplyr::across(
        c(feature_area_ha)
        , ~ sum(.x,na.rm = T)
      )
    ) %>% 
    dplyr::ungroup() %>% 
    dplyr::mutate(
      area_ha = feature_area_ha
      , area_ac = (area_ha*10000)/4046.85642
      , area_tot_ac = sum(area_ac)
      , area_tot_ha = sum(area_ha)
      , n_tot = sum(n)
      , n = scales::comma(n, accuracy = 1)
    ) %>% 
    dplyr::mutate(
      dplyr::across(
        tidyselect::starts_with("area_")
        , ~ scales::comma(.x, suffix = "k", scale = 1e-3, accuracy = 1)
      )
    )
hi_usfs_n <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="USFS-Only") %>% dplyr::pull(n)
hi_usfs_ac <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="USFS-Only") %>% dplyr::pull(area_ac)
hi_usfs_ha <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="USFS-Only") %>% dplyr::pull(area_ha)
hi_all_n <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="All-Lands") %>% dplyr::pull(n)
hi_all_ac <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="All-Lands") %>% dplyr::pull(area_ac)
hi_all_ha <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="All-Lands") %>% dplyr::pull(area_ha)
hi_tot_n <- hi_risk_brkdwn_temp %>% dplyr::filter(dplyr::row_number()==1) %>% dplyr::pull(n_tot)
hi_tot_ac <- hi_risk_brkdwn_temp %>% dplyr::filter(dplyr::row_number()==1) %>% dplyr::pull(area_tot_ac)
hi_tot_ha <- hi_risk_brkdwn_temp %>% dplyr::filter(dplyr::row_number()==1) %>% dplyr::pull(area_tot_ha)
```

```{r print-title, fig.height=1, fig.width=10, fig.asp=NULL, fig.align='left'}
title_plot_temp
```

```{r print-spatial-frmwrk, fig.asp=image_asp_temp}
# {r print-spatial-frmwrk, fig.height=height_for_image_temp, fig.width=width_for_image}
# spatial_frmwrk_map_temp
spatial_frmwrk_inset_temp +
  theme(
    plot.caption = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
  )
```
The `r area_name_nost` priority landscape (black outline) located in `r area_st` (see map inset) covers `r area_acres` acres (`r area_ha` ha). We used the nested spatial framework for firesheds (gray dashed outline; [Ager et al. (2021)](https://scholar.google.com/scholar?cluster=7852635540589253195&hl=en&as_sdt=0,6)) ~250,000 acres (100,000 ha) in size which are the broad scale unit of prioritization and nested fireshed project areas (light blue outline) ~25,000 acres (10,000 ha) in size which are used for planning and conducting vegetation management projects. Fireshed project areas are shaded by risk to communities of the parent fireshed with the highest risk firesheds selected in the USFS Wildfire Crisis Strategy shaded red (multiple ownerships) and orange (USFS ownership only). 

The `r area_name_nost` landscape includes `r ifelse(is.na(hi_tot_n), 0, hi_tot_n)` high-risk fireshed project areas (shaded red and orange) that cover `r ifelse(is.na(hi_tot_ac), 0, hi_tot_ac)` acres (`r ifelse(is.na(hi_tot_ha), 0, hi_tot_ha)` ha). There are `r ifelse(is.na(hi_usfs_n), 0, hi_usfs_n)` high-risk project areas managed solely by USFS (shaded orange) that cover `r ifelse(is.na(hi_usfs_ac), 0, hi_usfs_ac)` acres (`r ifelse(is.na(hi_usfs_ha), 0, hi_usfs_ha)` ha). There are `r ifelse(is.na(hi_all_n), 0, hi_all_n)` high-risk project areas managed by multiple owners (shaded red) that cover `r ifelse(is.na(hi_all_ac), 0, hi_all_ac)` acres (`r ifelse(is.na(hi_all_ha), 0, hi_all_ha)` ha).

\newpage

asdfasdf asdfasdf sadf asdf asdf astg dr gbdfagawert dfvgasdf adsf saedt dsafg aer tg fdg