---
# title: "`r params$area_name`"
title: ""
author: ""
date: ""
# date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  area_num: 5
  area_name: "Temp Name"
geometry: margin=1.5cm
output:
  pdf_document: default
  # bookdown::pdf_document2
linkcolor: blue
header-includes: |
    \usepackage{fancyhdr}
    \pagestyle{fancy}
    \fancyhead{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[CO,CE]{`r params$area_name`}
    \fancyfoot[LE,RO]{\thepage}
# header-includes:
#   - \usepackage{caption}
#   - \captionsetup[figure]{labelformat=empty}
# editor_options: 
#   chunk_output_type: console
# knit: (function(inputFile, encoding){ 
#     out_dir <- '/';
#     rmarkdown::render(inputFile, encoding = encoding, output_file=file.path(dirname(inputFile), out_dir, 'ECOL592_RDAandCCA_GWoolsey.pdf')) 
#   })
---

```{r, include=F, warning=F, message=F, echo=F}
# knit options
knitr::opts_chunk$set(
  echo = FALSE
  , warning = FALSE
  , message = FALSE
  , include = TRUE
  , eval = TRUE
  , fig.asp = 0.8
  , fig.width = 7
  # , fig.height = 8
  , fig.align = 'center'
)
remove(list = ls()[grep("_temp",ls())])
gc()
```

```{r call-fns}
##################################################
##################################################
# set the figure size
##################################################
##################################################
bb_temp <- wf_landscapes %>% 
  dplyr::filter(area_name==area_nm_list[params$area_num]) %>% 
  sf::st_transform(3857) %>% 
  sf::st_bbox()
w_temp <- bb_temp[3] - bb_temp[1]
h_temp <- bb_temp[4] - bb_temp[2]
# fig.asp sets the height-to-width ratio
image_asp_temp <- min(h_temp/w_temp,1)
# change the sizing of the basemap using theme_light(base_size = base_size_temp)
base_size_temp = ifelse(image_asp_temp==1,8,9)
# change the subtitle labels created with ggtext for layered constraints plot
ggtext_size_temp = ifelse(image_asp_temp==1,7,10)
# change the fig.asp for the treatable_map_fn figure since this is now wider than single map
image_asp_facet_temp <- max(image_asp_temp*ifelse(image_asp_temp==1,0.65,0.55),0.35)
# width_for_image <- round(((21.59-2*2)/2.54),1) # max width of 21.59cm page with 2cm margin (converted to in)
# height_for_image_temp <- round((width_for_image * h_temp) / w_temp, 1)
##################################################
##################################################
# call all the functions
##################################################
##################################################
# set aggregate factor for raster data
  agg_fact_temp <- 20
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  plt_basemap <<- landscape_basemap_fn(row_n = params$area_num, my_base_size = base_size_temp)
# load raster data
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  rast_list_temp <<- raster_data_read_fn(row_n = params$area_num)
  # rast_list_temp <- raster_data_read_fn(row_n = params$area_num)
#################
# PLOTS
#################
title_plot_temp <- title_plot_fn(row_n = params$area_num)
# spatial_frmwrk_map_temp <- spatial_frmwrk_map_fn(row_n = params$area_num)
spatial_frmwrk_inset_temp <- spatial_frmwrk_inset_fn(row_n = params$area_num)
# rast_area_fn(row_n = params$area_num, layer_name = "is_treatable")
landcover_map_temp <- landcover_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
protected_map_temp <- protected_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
slopes_map_temp <- slopes_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
roads_map_temp <- roads_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
riparian_map_temp <- riparian_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
administrative_map_temp <- administrative_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
# area available and constraint reduction table
treatable_map_temp <- treatable_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp)
reduction_table_temp <- reduction_table_fn(row_n = params$area_num)
reduction_kable_temp <- reduction_kable_fn(row_n = params$area_num)
# fireshed project area plots
plt_fshed_cnstrnt_lvl_temp <- plt_fshed_cnstrnt_lvl_fn(row_n = params$area_num)
largest_patch_map_temp <- largest_patch_map_fn(row_n = params$area_num)
plt_patch_prop_temp <- plt_patch_prop_fn(row_n = params$area_num)
plt_obj_trtbl_temp <- plt_obj_trtbl_fn(row_n = params$area_num)
# names and labels
area_name_nost <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(name)
area_st <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(state)
area_acres <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(acres) %>% 
  scales::comma(suffix = "k", scale = 1e-3, accuracy = 1)
area_ha <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(hectares) %>% 
  scales::comma(suffix = "k", scale = 1e-3, accuracy = 1)
####### high-risk area calculations
# usfs vs all lands
hi_risk_brkdwn_temp <-
  constrained_by_scnro_ls_pa %>% 
    dplyr::filter(
      pct_pa_intrsct>=0.25
      & area_name == area_nm_list[params$area_num]
      & fireshed_crisis_strategy %in% c("USFS-Only", "All-Lands")
      & scenario_id == 1
    ) %>% 
    dplyr::group_by(fireshed_crisis_strategy) %>% 
    dplyr::summarise(
      n = n()
      , dplyr::across(
        c(feature_area_ha)
        , ~ sum(.x,na.rm = T)
      )
    ) %>% 
    dplyr::ungroup() %>% 
    dplyr::mutate(
      area_ha = feature_area_ha
      , area_ac = (area_ha*10000)/4046.85642
      , area_tot_ac = sum(area_ac)
      , area_tot_ha = sum(area_ha)
      , n_tot = sum(n)
      , n = scales::comma(n, accuracy = 1)
    ) %>% 
    dplyr::mutate(
      dplyr::across(
        tidyselect::starts_with("area_")
        , ~ scales::comma(.x, suffix = "k", scale = 1e-3, accuracy = 1)
      )
    )
hi_usfs_n <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="USFS-Only") %>% dplyr::pull(n)
hi_usfs_ac <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="USFS-Only") %>% dplyr::pull(area_ac)
hi_usfs_ha <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="USFS-Only") %>% dplyr::pull(area_ha)
hi_all_n <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="All-Lands") %>% dplyr::pull(n)
hi_all_ac <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="All-Lands") %>% dplyr::pull(area_ac)
hi_all_ha <- hi_risk_brkdwn_temp %>% dplyr::filter(fireshed_crisis_strategy=="All-Lands") %>% dplyr::pull(area_ha)
hi_tot_n <- hi_risk_brkdwn_temp %>% dplyr::filter(dplyr::row_number()==1) %>% dplyr::pull(n_tot)
hi_tot_ac <- hi_risk_brkdwn_temp %>% dplyr::filter(dplyr::row_number()==1) %>% dplyr::pull(area_tot_ac)
hi_tot_ha <- hi_risk_brkdwn_temp %>% dplyr::filter(dplyr::row_number()==1) %>% dplyr::pull(area_tot_ha)
```

```{r print-title, fig.height=1, fig.width=10, fig.asp=NULL, fig.align='left'}
title_plot_temp
```

```{r print-spatial-frmwrk, fig.asp=image_asp_temp}
# {r print-spatial-frmwrk, fig.height=height_for_image_temp, fig.width=width_for_image}
# spatial_frmwrk_map_temp
spatial_frmwrk_inset_temp +
  theme(
    plot.caption = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
  )

# The full process for delineating fireshed boundaries and determining risk across the continental US is described in detail in [Ager et al. (2021)](https://scholar.google.com/scholar?cluster=7852635540589253195&hl=en&as_sdt=0,6).
```
The `r area_name_nost` priority landscape (black outline) located in `r area_st` (see map inset) covers `r area_acres` acres (`r area_ha` ha). We used the nested spatial framework for firesheds (gray dashed outline; [Ager et al. (2021)](https://scholar.google.com/scholar?cluster=7852635540589253195&hl=en&as_sdt=0,6)) ~250,000 acres (100,000 ha) in size which are the broad scale unit of prioritization and nested fireshed project areas (light blue outline) ~25,000 acres (10,000 ha) in size which are used for planning and conducting vegetation management projects. Fireshed project areas are shaded by risk to communities of the parent fireshed with the highest risk firesheds selected in the USFS Wildfire Crisis Strategy shaded red (multiple ownerships) and orange (USFS ownership only). 

The `r area_name_nost` landscape includes `r ifelse(is.na(hi_tot_n), 0, hi_tot_n)` high-risk fireshed project areas (shaded red and orange) that cover `r ifelse(is.na(hi_tot_ac), 0, hi_tot_ac)` acres (`r ifelse(is.na(hi_tot_ha), 0, hi_tot_ha)` ha). There are `r ifelse(is.na(hi_usfs_n), 0, hi_usfs_n)` high-risk project areas managed solely by USFS (shaded orange) that cover `r ifelse(is.na(hi_usfs_ac), 0, hi_usfs_ac)` acres (`r ifelse(is.na(hi_usfs_ha), 0, hi_usfs_ha)` ha). There are `r ifelse(is.na(hi_all_n), 0, hi_all_n)` high-risk project areas managed by multiple owners (shaded red) that cover `r ifelse(is.na(hi_all_ac), 0, hi_all_ac)` acres (`r ifelse(is.na(hi_all_ha), 0, hi_all_ha)` ha).

\newpage

```{r print-layered-constraints}
(landcover_map_temp + 
  protected_map_temp + 
  slopes_map_temp + 
  roads_map_temp + 
  riparian_map_temp + 
  administrative_map_temp) +
  patchwork::plot_layout(
    ncol = 3
    # , widths = c(1, 2)
  ) +
  patchwork::plot_annotation(tag_levels = 'A') & 
  theme(
    plot.title = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
    , plot.subtitle = ggtext::element_markdown(size = ggtext_size_temp)
  )  
# to get plots to overlap ;)
# G3 <- G1 + plot_spacer() + G2 + plot_layout(widths = c(4, -1.1 ,4.5),guides = "collect")& theme(legend.position = "top")
```

Layered operational constraints were considered in order to quantify the amount of land available for mechanical forest health and risk reduction fuel treatments. The analysis identifies (A) all forest and shrubland areas, (B) removes protected and inventoried roadless areas (IRA), (C) classifies land as mechanically operable based on terrain slope, (D) buffers existing roads according to equipment haul distance, (E) removes areas within riparian buffers, (F) removes areas within administrative boundaries to determine what land is mechanically available or constrained and by what factor.

```{r table-reductions, fig.height=2, fig.width=9.5, fig.asp=NULL}
# ```{r table-reductions, fig.height=2}
# reduction_kable_temp
reduction_table_temp + 
  theme(
    plot.title = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
  )
```

```{r treatable-map, fig.asp=image_asp_facet_temp}
# ```{r treatable-map, fig.height=6.5}
treatable_map_temp +
  theme(
    plot.title = element_blank()
    , plot.margin = margin(0,0,0,0,"cm")
    , plot.subtitle = ggtext::element_markdown(size = ggtext_size_temp)
  )
```

The proportion of combined forest and shrubland area available for mechanical treatment was calculated by considering layered operational constraints on mechanical treatment based on three scenarios using current standards. At each level of constraint, the reduction in area and percentage was calculated based on the area remaining after considering the cumulative impact of prior constraints.

\newpage

```{r fshed-cnstrnt-dist, fig.asp=0.36, fig.width=7}
# ```{r fshed-cnstrnt-dist, fig.height=3, fig.width=11}
plt_cnstrnt_class_table +
plt_fshed_cnstrnt_lvl_temp +
  theme(
    legend.position = "bottom"
    , legend.margin = margin(-0.3,0.0,0.0,0.0, "cm")
    , plot.title = element_blank()
    , plot.margin = margin(0.0,0.0,0.0,0.2, "cm")
    , axis.title.x = element_text(size=6)
  ) +
  patchwork::plot_layout(nrow = 1, widths = c(1,1.45)) 
```

Levels of mechanical constraint used to classify fireshed project areas were chosen based on USFS Wildfire Crisis Strategy objectives and science showing that fuels treatments are more effective as the percentage of the landscape treated progressively increases. We then calculated the proportion of fireshed project areas in each of these mechanical constraint classes both within the overall landscape area and within high-risk firesheds only.

```{r largest-patch-map, fig.asp=image_asp_facet_temp}
# ```{r largest-patch-map, fig.asp=image_asp_facet_temp}
largest_patch_map_temp +
  plt_patch_prop_temp +
  patchwork::plot_layout(ncol = 1, heights = c(1,0.2)) &
  theme(
    legend.position = "none"
    , plot.title = element_blank()
    , plot.margin = margin(0,0,0,0, "cm")
  )
```

We selected the largest patch of interconnected fireshed project areas by constraint class and calculated the percent of the area of the overall landscape comprised by this patch (i.e., largest patch index).Comparison is made between the largest patch of project areas classified as high constraint (100–81% constrained; 0–19% available for mechanical treatment) and the largest patch of project areas classified as low constraint (0–59% constrained; 41–100% available). Extensive patches with little mechanical constraint represent opportunities for land managers to design plans that incorporate the principles of effective landscape-scale fuel treatments.

```{r obj-trtbl, fig.asp=0.25, fig.width=7}
plt_obj_trtbl_temp +
  theme(
    plot.title = element_blank()
    , plot.margin = margin(0.0,0.0,0.0,0.0, "cm")
    , axis.text.y = element_text(size=9)
  )
```

sdafasdgfafdg asdf asdgterhg sad sdafasdgfafdg asdf asdgterhg sad sdafasdgfafdg asdf asdgterhg sad sdafasdgfafdg asdf asdgterhg sad sdafasdgfafdg asdf asdgterhg sad sdafasdgfafdg asdf asdgterhg sad sdafasdgfafdg asdf asdgterhg sad 

```{r, eval=FALSE, include=FALSE}
  (plt_scenario_table +
     patchwork::plot_spacer()
  ) /
  reduction_table_fn(1) +
  patchwork::plot_layout(ncol = 1)
# & theme(plot.margin = margin(0,0,0,0,"cm"))
ggplot2::ggsave(paste0("C:/Users/georg/Downloads/hey_xxx.jpeg"),width = 8.8, height = 3.5, units = "in")


# Testing
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  plt_basemap <<- landscape_basemap_fn(row_n = 5)
# load raster data
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  rast_list_temp <<- raster_data_read_fn(row_n = 5)
  # rast_list_temp <- raster_data_read_fn(row_n = 5)
# PLOTS
landscape_basemap_temp <- landscape_basemap_fn(row_n = 5)
spatial_frmwrk_map_temp <- spatial_frmwrk_map_fn(row_n = 5)
# rast_area_fn(row_n = 5, layer_name = "is_treatable")
landcover_map_temp <- landcover_map_fn(row_n = 5, rast_agg_fact = 9)
protected_map_temp <- protected_map_fn(row_n = 5, rast_agg_fact = 9)
slopes_map_temp <- slopes_map_fn(row_n = 5, rast_agg_fact = 9)
roads_map_temp <- roads_map_fn(row_n = 5, rast_agg_fact = 9)
riparian_map_temp <- riparian_map_fn(row_n = 5, rast_agg_fact = 9)
administrative_map_temp <- administrative_map_fn(row_n = 5, rast_agg_fact = 9)
treatable_map_temp <- treatable_map_fn(row_n = 5, rast_agg_fact = 9)
reduction_table_temp <- reduction_table_fn(row_n = 5)
title_plot_temp <- title_plot_fn(row_n = 5)
scenario_cnstrnt_map_temp <- scenario_cnstrnt_map_fn(row_n = 5)
largest_patch_map_temp <- largest_patch_map_fn(row_n = 5)
plt_patch_prop_temp <- plt_patch_prop_fn(row_n = 5)
plt_fshed_cnstrnt_lvl_temp <- plt_fshed_cnstrnt_lvl_fn(row_n = 5)
#####################################################################
landscape_basemap_temp
spatial_frmwrk_map_temp
landcover_map_temp
protected_map_temp
slopes_map_temp
roads_map_temp
riparian_map_temp
administrative_map_temp
treatable_map_temp
reduction_table_temp
title_plot_temp
scenario_cnstrnt_map_temp
largest_patch_map_temp
plt_patch_prop_temp
plt_fshed_cnstrnt_lvl_temp
# CLEAN
remove(list = ls()[grep("_temp",ls())])
gc()

```

