---
title: "WCS Info Packet for `r area_nm_list[params$area_nm]`"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  area_num: 5
output: pdf_document
# linkcolor: blue
# header-includes:
#   - \usepackage{caption}
#   - \captionsetup[figure]{labelformat=empty}
# editor_options: 
#   chunk_output_type: console
# knit: (function(inputFile, encoding){ 
#     out_dir <- '/';
#     rmarkdown::render(inputFile, encoding = encoding, output_file=file.path(dirname(inputFile), out_dir, 'ECOL592_RDAandCCA_GWoolsey.pdf')) 
#   })
---

```{r, include=F, warning=F, message=F, echo=F}
# knit options
knitr::opts_chunk$set(
  echo = FALSE
  , warning = FALSE
  , message = FALSE
  , include = TRUE
  , eval = TRUE
  , fig.width = 10
  , fig.height = 8
)
remove(list = ls()[grep("_temp",ls())])
gc()
```

```{r call-fns}
# set aggregate factor for raster data
  agg_fact_temp <- 12
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  plt_basemap <<- landscape_basemap_fn(row_n = params$area_num)
# load raster data
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  rast_list_temp <<- raster_data_read_fn(row_n = params$area_num)
  # rast_list_temp <- raster_data_read_fn(row_n = params$area_num)
# PLOTS
spatial_frmwrk_map_temp <- spatial_frmwrk_map_fn(row_n = params$area_num)
# rast_area_fn(row_n = params$area_num, layer_name = "is_treatable")
landcover_map_temp <- landcover_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp) +
  theme(plot.title = element_blank())
protected_map_temp <- protected_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp) +
  theme(plot.title = element_blank())
slopes_map_temp <- slopes_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp) +
  theme(plot.title = element_blank())
roads_map_temp <- roads_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp) +
  theme(plot.title = element_blank())
riparian_map_temp <- riparian_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp) +
  theme(plot.title = element_blank())
administrative_map_temp <- administrative_map_fn(row_n = params$area_num, rast_agg_fact = agg_fact_temp) +
  theme(plot.title = element_blank())
# names and labels
area_name_nost <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(name)
area_st <- wf_landscapes %>% 
  sf::st_drop_geometry() %>% 
  dplyr::filter(area_name == area_nm_list[params$area_num]) %>% 
  dplyr::pull(state)
```

Nested spatial framework of the `r area_name_nost` (`r area_st`; black outline) delineating firesheds (gray dashed outline) approximately 100,000 hectares (250,000 acres) in size which are the broad scale unit of prioritization and nested fireshed project areas (light blue outline) approximately 10,000 hectares (25,000 acres) in size which are used for planning and conducting fuel management projects. Fireshed project areas are shaded by risk to communities of the parent fireshed with the highest risk firesheds as determined by the Strategy shaded red (multiple ownerships) and orange (USFS ownership only). The full process for delineating fireshed boundaries across the continental US is described in detail in [Ager et al. (2021)](https://scholar.google.com/scholar?cluster=7852635540589253195&hl=en&as_sdt=0,6).

```{r print-spatial-frmwrk}
spatial_frmwrk_map_temp
```

Workflow used to quantify the amount of land available for mechanical forest health and risk reduction fuel treatments by considering layered operational constraints. The analysis identifies (A) all forest and shrubland areas, (B) removes protected and inventoried roadless areas, (C) classifies land as mechanically operable based on terrain slope, (D) buffers existing roads according to equipment haul distance, (E) removes areas within riparian buffers, (F) removes areas within administrative boundaries to determine what land is mechanically available or constrained and by what factor.

```{r print-layered-constraints}
(landcover_map_temp + protected_map_temp + slopes_map_temp) /
  (roads_map_temp + riparian_map_temp + administrative_map_temp) +
  patchwork::plot_annotation(tag_levels = 'A')
```

```{r, eval=FALSE, include=FALSE}
# Testing
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  plt_basemap <<- landscape_basemap_fn(row_n = 5)
# load raster data
# !!!!!!!!!THIS IS SET GLOBALLY!!!!!!!!!
  rast_list_temp <<- raster_data_read_fn(row_n = 5)
  # rast_list_temp <- raster_data_read_fn(row_n = 5)
# PLOTS
landscape_basemap_temp <- landscape_basemap_fn(row_n = 5)
spatial_frmwrk_map_temp <- spatial_frmwrk_map_fn(row_n = 5)
# rast_area_fn(row_n = 5, layer_name = "is_treatable")
landcover_map_temp <- landcover_map_fn(row_n = 5, rast_agg_fact = 9)
protected_map_temp <- protected_map_fn(row_n = 5, rast_agg_fact = 9)
slopes_map_temp <- slopes_map_fn(row_n = 5, rast_agg_fact = 9)
roads_map_temp <- roads_map_fn(row_n = 5, rast_agg_fact = 9)
riparian_map_temp <- riparian_map_fn(row_n = 5, rast_agg_fact = 9)
administrative_map_temp <- administrative_map_fn(row_n = 5, rast_agg_fact = 9)
treatable_map_temp <- treatable_map_fn(row_n = 5, rast_agg_fact = 9)
reduction_table_temp <- reduction_table_fn(row_n = 5)
title_plot_temp <- title_plot_fn(row_n = 5)
scenario_cnstrnt_map_temp <- scenario_cnstrnt_map_fn(row_n = 5)
largest_patch_map_temp <- largest_patch_map_fn(row_n = 5)
plt_patch_prop_temp <- plt_patch_prop_fn(row_n = 5)
plt_fshed_cnstrnt_lvl_temp <- plt_fshed_cnstrnt_lvl_fn(row_n = 5)
#####################################################################
landscape_basemap_temp
spatial_frmwrk_map_temp
landcover_map_temp
protected_map_temp
slopes_map_temp
roads_map_temp
riparian_map_temp
administrative_map_temp
treatable_map_temp
reduction_table_temp
title_plot_temp
scenario_cnstrnt_map_temp
largest_patch_map_temp
plt_patch_prop_temp
plt_fshed_cnstrnt_lvl_temp
# CLEAN
remove(list = ls()[grep("_temp",ls())])
gc()

```

